Arterial pulsations cannot drive intramural periarterial drainage: Significance for \Ab drainage

### 2017-07-29 paper.tex
reviewers comments

\title[Arterial pulsations cannot drive periarterial drainage]{Arterial pulsations cannot drive intramural periarterial drainage: Significance for Alzheimer's disease}

@@

The results from this study showed that the average drainage flux of ISF is \SI{-1.12e-2}{\cubic\micro\metre\per\second} at $r = r_0 + 0h$ and $K_0/K_1 = 0.01$. This value indicates a net reverse flow within the BM, although it is eight orders of magnitude smaller than the flux of \SI{0.001}{\cubic\milli\metre\per\second} estimated by \cite{Arbel-Ornath2013}. The results therefore suggest that arterial pulsations are not powerful enough to drive perivascular drainage of ISF through the BM. This is due to the very long wavelength of the arterial pulsations compared to the artery section considered, which results in very small pressure gradients along the vessel length (Figure~\ref{fig:mca}b). These results are confirmed here by analysing the pattern of IPAD in mice after administration of pulse modulators. No significant differences were found between mice that received the pulse modulator and control mice. It appears that other forces are neccessary to produce the pressure gradients required to push fluid through the BM and an interesting candidate for such forces is the contraction of vascular smooth muscle cells, as noted in \cite{DiMarco2015} and modelled in detail by \cite{Aldea2016}.

>>>>

\title[Arterial pulsations cannot drive periarterial drainage]{Arterial pulsations cannot drive intramural periarterial drainage: Significance for \Ab drainage}

@@

The results from this study showed that the average drainage flux of ISF is \SI{-1.12e-2}{\cubic\micro\metre\per\second} at $r = r_0 + 0h$ and $K_0/K_1 = 0.01$. This value indicates a net reverse flow within the BM, although it is eight orders of magnitude smaller than the flux of \SI{0.001}{\cubic\milli\metre\per\second} estimated by \cite{Arbel-Ornath2013}. The results therefore suggest that arterial pulsations are not powerful enough to drive perivascular drainage of ISF through the BM. This is due to the very long wavelength of the arterial pulsations compared to the artery section considered, which results in very small pressure gradients along the vessel length (Figure~\ref{fig:mca}b). These results are confirmed here by analysing the pattern of IPAD in mice after administration of pulse modulators. No significant differences were found between mice that received the pulse modulator and control mice. We were unable to measure whether the treatment of mice did not, in addition to the desired reduction in pulsation frequency, lead to a decrease in the magnitude of pulsations. However, given that the flow rate calculated from the computational model is eight orders of magnitude smaller than what would have been expected it is highly unlikely that the administration of the beta-blocker caused a pressure drop large enough to solely cause this discrepancy in flow rates. It appears that other forces are neccessary to produce the pressure gradients required to push fluid through the BM and an interesting candidate for such forces is the contraction of vascular smooth muscle cells, as noted in \cite{DiMarco2015} and modelled in detail by \cite{Aldea2016}.
